Modalities for Virtualizing Memory Addresses

### 2022-09-26 programlogic.tex
+
STOP: until discussing with Colin

\begin{figure}

@@

  \quad \exists_{\tlfoff\Locn \;, \tltoff\Locn \;, \tltwoff\Locn \;,} \\
  \quad \exists_{\tlooff\Locn \;, \tpgoff\Loctw \;, \tlt\Loc \;, \tltw\Loc \;, \tlo\Loc \tpg\Loc} \ldotp\\
  \quad \ulcorner \textsf{aligned } \vaddr \urcorner \star\\
  \quad \ulcorner \vaddr = \locsx ++ \lfoff ++ \ltoff ++ \\
  \qquad\qquad \qquad \ltwoff ++ \looff ++ \pgoff \urcorner \star\\
  \quad  \pfpointsto{\lvlsum\crt\lfoff}{\lvlbor\lt}\qfrac\ppts \star \\
  \quad  \pfpointsto{\lvlsum\lt\ltoff}{\lvlbor\ltw}\qfractw\ppts \star \\
  \quad \pfpointsto{\lvlsum\ltw\ltwoff}{\lvlbor\lo}\qfract\ppts \star \\
  \quad \pfpointsto{\lvlsum\lo\looff}{\lvlbor\pg}\qfracf\ppts \star \\
  \quad \ppointsto{\pageptstosum\pg\pgoff}\locsf\ppts 

@@

@@

\subsection{Reasoning Rules for Selected Instructions}
\label{sec:reasoning}
\input{fig-reasoning}
As is usual in \SL, the reasoning rules of the program logic allow deriving
Hoare triples of the form $\triple\pre\instr\post$, where the
precondition~$\pre$ and the postcondition~$\post$ are assertions,
and where $i$ is an instruction.
Such a triple receives a standard interpretation as a statement of partial
correctness: the assertion $\triple\pre\instr\post$ means that, in a state
where $\pre$ holds, it is safe to execute the instruction~$\instr$, and if
this execution terminates, then it leads to a final state where $\post$ holds.
A more precise statement is given in the next section (\sref{sec:soundness}).
\mytodo{iso todo: talk about each rule and change the intro to this subsection}
\subsection{Modal Abstraction for Virtualizing Memory Locations}

@@

  \item \textbf{contingency}: the fact $\modalP$ abstracts the memory address mappings \textit{under} the address space rooted at $\ell$ (e.g. $\crt$)

@@

  \item \textbf{interaction with ambient logic for a local-state}: \mytodo{talk about this issue's vitality in this paper with Colin}

@@

To concretize the understanding of these principles achieved with the modal abstraction for address-space, $\modaldef\ell\modalP$, let us first investigate the specification of the instruction ($\textsf{movctl\_instr}$) switching address spaces. Assume that our CPU keeps the current address space based on its page table register CR3, as we see in Figure \fref{fig:addressspaceswitching}.
\input{fig-ctlreasoning}
Thinking of $\modalP$ and $\modalQ$ as resources representing the indirection mappings ($\mapsto_{\kw{p}}$) in the address spaces rooted at $\rvsrc$ and $\rvdst$ respectively, the rule interacts with the ambient logic, \SL, via pulls local state out of the address-space modality rooted at $\rvdst$, and make it the observable view of the memory.

\todo[inline]{We don't need to talk about sexec at all. Let's also talk tomorrow about adjusting the syntax in the paper to mimic actual textual assembly more closely (e.g., all of the instructions are mov, with different argument shapes)}

\mytodo{STOP HERE}

>>>>

\begin{figure*}

@@

  \exists_{\tlfoff\Locn \;, \tltoff\Locn \;, \tltwoff\Locn \;,\tlooff\Locn \;, \tpgoff\Loctw \;, \tlt\Loc \;, \tltw\Loc \;, \tlo\Loc \tpg\Loc} \ldotp \\
  \ulcorner \textsf{aligned } \vaddr \urcorner \star 
   \ulcorner \vaddr = \locsx :: \lfoff :: \ltoff :: 
   \ltwoff :: \looff :: \pgoff \urcorner \star\\
  \pfpointsto{\lvlsum\crt\lfoff}{\lvlbor\lt}\qfracfotsss\ppts \star 
  \pfpointsto{\lvlsum\lt\ltoff}{\lvlbor\ltw}\qfracfotss\ppts \star \\
  \pfpointsto{\lvlsum\ltw\ltwoff}{\lvlbor\lo}\qfracfots\ppts \star 
  \pfpointsto{\lvlsum\lo\looff}{\lvlbor\pg}\qfracfot\ppts \star \\
  \ppointsto{\pageptstosum\pg\pgoff}\locsf\ppts 

@@

\end{figure*}
\paragraph{Coalescing and Coexistence} \mytodo{Super Huge pages}

@@

\subsection{Reasoning with Modal Abstraction for Virtual Memory Locations}

@@

  \item \textbf{locality}: the fact $\modalP$ abstracts the memory address mappings \textit{under} the address space rooted \textit{at} $\ell$ (e.g. $\crt$)

@@

@@

\paragraph{Interaction with Ambient Logic for Local State} To concretize the understanding of these principles achieved with the modal abstraction for address-space, $\modaldef\ell\modalP$, let us first investigate the specification of the instruction ($\textsf{movctl\_instr}$) switching address spaces. Assume that our CPU keeps the current address space based on its page table register CR3, as we see in Figure \fref{fig:addressspaceswitching}.
\input{fig-ctlreasoning}
Thinking of $\modalP$ and $\modalQ$ as resources representing the indirection mappings ($\mapsto_{\kw{p}}$) in the address spaces rooted at $\rvsrc$ and $\rvdst$ respectively, the rule interacts with the ambient logic, \SL, via pulls local state out of the address-space modality rooted at $\rvdst$, and make it the observable view of the memory.

\paragraph{Copying, Expanding and Shrinking}
\todo[inline]{We don't need to talk about sexec at all. Let's also talk tomorrow about adjusting the syntax in the paper to mimic actual textual assembly more closely (e.g., all of the instructions are mov, with different argument shapes)}

\paragraph{Self-Mapping Location Virtualization}
